---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggtextparallels

The goal of ggtextparallels is to approximate fancy and expensive tools like the *Synopsis Quattuor Evangeliorum*, an essential tool for biblical scholars. `ggtextparallels` supports both the English and Greek texts.

## Installation

`ggtextparallels` is not on CRAN, but can be installed with `devtools`:

```{r eval=FALSE}
devtools::install_github("daranzolin/ggtextparallels")
library(ggtextparallels)
```

## Examples

The central function, `ggtextparallel`, takes three arguments: a `parallel_no`, which can be gleaned from `gospel_parallels`, `lang`, the language argument, and `words_per_row`, which allows users to adjust the amount of words displayed on each row.

156 gospel parallels are available:

```{r echo=FALSE}
library(ggtextparallels)
head(gospel_parallels)
```

Here I request the English parallel of 'The Healing of Peter's Mother-in-Law':

```{r example, fig.width=12}
ggtextparallel(parallel_no = 37, lang = "eng", words_per_row = 6)
```

Words common to each pericope are listed in the plot caption.

I can view the Greek by flipping the `lang` argument:

```{r, fig.width=12}
ggtextparallel(37, "grc", 5)
```


## Future Work

* Tests
* Vignette
* Better organization of text
* Highlighting similarities/differences
* Document similarity scores in caption
