---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggtextparallels

The goal of ggtextparallels is to approximate fancy and expensive tools like the *Synopsis Quattuor Evangeliorum*, an essential tool for biblical scholars. `ggtextparallels` supports both the English and Greek texts.

## Installation

`ggtextparallels` is not on CRAN, but can be installed with `devtools`:

```{r eval=FALSE}
devtools::install_github("daranzolin/ggtextparallels")
```

## Examples

The central function, `ggtextparallel`, takes two arguments: a `parallel_no`, which can be gleaned from `gospel_parallels`, and `lang`, the language argument.

156 gospel parallels are available:

```{r echo=FALSE}
library(ggtextparallels)
head(gospel_parallels)
```

English:

```{r example, fig.width=12}
library(ggtextparallels)
ggtextparallel(37)
```

Greek:

```{r, fig.width=12}
ggtextparallel(37, lang = "grc")
```


## Future Work

* Tests
* Vignette
* Better organization of text
* Highlighting similarities/differences
* Document similarity scores in caption
